%-------------------------
% Resume in Latex - Luis Alarcon (PM-focused version with YourOwn)
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\begin{document}
\begin{center}
    \textbf{\Huge \scshape Luis Alarcon} \\ \vspace{1pt}
    \small 936-828-9969 $|$ \href{mailto:alarconMandujanoLuis@gmail.com}{\underline{alarconMandujanoLuis@gmail.com}} $|$
    \href{https://www.linkedin.com/in/luis-alberto-alarcon-mandujano-68316b359}{\underline{linkedin}} $|$
    \href{https://github.com/LuisAlar}{\underline{github}} 

\end{center}
{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Dallas}{Dallas, TX}
      {Bachelor of Science in Software Engineering}{Expected May 2027}

  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Orbital Mentorship}{Nov 2024 -- Present}
      {DevOps Lead}{}
      \resumeItemListStart
        \resumeItem{\textbf{Engineered an AI-assisted workflow automation} to streamline developer onboarding. Defined operational requirements and managed the implementation of containerized environments, reducing configuration time by \textbf{50\%} and ensuring a repeatable setup process.}
        \resumeItem{Optimized data retrieval workflows by redesigning the client data flow and establishing a centralized API layer, lowering network request volume and significantly \textbf{improving} operational efficiency.}
        \resumeItem{Built an in-house API observability layer to identify frontend over-fetching, translating unstructured system metrics into clear, actionable insights for developers.}
      \resumeItemListEnd
    \resumeSubheading
      {Xtensible Solutions}{Apr 2024 -- Aug 2024}
      {Solutions Engineer Intern}{}
      \resumeItemListStart
        \resumeItem{\textbf{Automated} operational workflows by designing a Python-based execution service for instance creation and snapshot management, significantly \textbf{reducing} manual developer overhead.}
        \resumeItem{Built and maintained comprehensive API testing architectures, \textbf{validating workflows across edge cases} to ensure accuracy, stability, and repeatability in production environments.}
        \resumeItem{Engineered detailed documentation and reliable quality assurance processes, translating complex technical inputs into clear, actionable insights for engineering leadership.}
      \resumeItemListEnd
    \resumeSubheading
      {Indigo Magazine}{Dec 2023 -- Present}
      {Web Development Officer \& Creative Director}{}
      \resumeItemListStart
        \resumeItem{Developed an end-to-end \textbf{automated workflow} for article submission and formatting, transforming unstructured inputs from writers into standardized outputs, dramatically \textbf{reducing publication lead time}.}
        \resumeItem{Architected a \textbf{process orchestration workflow} to automatically sync asset repositories, migrating media from a static codebase to a Cloudflare CDN by fetching unstructured inputs from Box.}
        \resumeItem{Spearheaded a comprehensive homepage redesign and optimized user engagement workflows, successfully adding \textbf{400+} new active users to the platform within the first month.}
      \resumeItemListEnd
    \resumeSubheading
      {Society of Hispanic Professional Engineers}{Oct 2023 -- Apr 2024}
      {Corporate Liaison}{}
      \resumeItemListStart
        \resumeItem{Secured \textbf{\$300} in funding through corporate partnerships to support student initiatives.}
        \resumeItem{Coordinated and hosted professional engagement events, expanding member access to networking and career opportunities.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{YourOwn} $|$ \emph{Team Lead \& System Architect}}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Automated} data validation workflows by integrating \textbf{AI-generated test suites}, continuously verifying data logic and state synchronization to ensure system reliability across edge cases.}
        \resumeItem{Managed dynamic UI configurations by implementing a structured drag-and-drop system, automating content management and ensuring 100\% data consistency across portfolios.}
        \resumeItem{Spearheaded the transition from a monolithic structure to an enterprise feature-based architecture, documenting structural logic to improve system maintainability and support long-term reuse.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical:} React, JavaScript, TypeScript, Java, Express, Prisma, Mongodb, Python, Docker, AWS, Postman \\
     \textbf{Design \& PM Tools:} Figma, Notion, Jira, Agile Workflow, UX Wireframing \\
     \textbf{Languages:} English, Spanish
    }}
 \end{itemize}
\end{document}

