%-------------------------
% Resume in Latex - Luis Alarcon (PM-focused version with YourOwn)
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\begin{document}
\begin{center}
    \textbf{\Huge \scshape Luis Alarcon} \\ \vspace{1pt}
    \small 936-828-9969 $|$ \href{mailto:alarconMandujanoLuis@gmail.com}{\underline{alarconMandujanoLuis@gmail.com}} $|$
    \href{https://www.linkedin.com/in/luis-alberto-alarcon-mandujano-68316b359}{\underline{linkedin}} $|$
    \href{https://github.com/LuisAlar}{\underline{github}} 

\end{center}
{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Dallas}{Dallas, TX}
      {Bachelor of Science in Software Engineering}{Expected May 2027}

  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Orbital Mentorship}{Nov 2024 -- Present}
      {Support/DevOps Lead}{}
      \resumeItemListStart
        \resumeItem{\textbf{Diagnosed and resolved complex software application issues} by building an API observability layer, identifying root causes of frontend over-fetching and translating technical metrics into actionable insights.}
        \resumeItem{\textbf{Triaged system bottlenecks} and collaborated with developers to redesign the client data flow, reducing network requests from 20 to 1-2 and significantly improving platform-wide load times.}
        \resumeItem{Created \textbf{user-friendly technical documentation} and containerized environments to streamline developer onboarding workflows, providing clear guidance and reducing setup time by 50\%.}
      \resumeItemListEnd
    \resumeSubheading
      {Xtensible Solutions}{Apr 2024 -- Aug 2024}
      {Solutions Engineer Intern}{}
      \resumeItemListStart
        \resumeItem{Performed comprehensive \textbf{functionality and system testing}, continuously monitoring API workflows to diagnose expected and edge-case behaviors during non-peak support times.}
        \resumeItem{Tracked and documented technical defects through exploratory testing, ensuring \textbf{timely resolution of software issues} and providing continuous feedback to engineering management.}
        \resumeItem{Leveraged automation tools to manage cloud instances and snapshot retrieval, independently prioritizing constraints to maintain service efficiency.}
      \resumeItemListEnd
    \resumeSubheading
      {Indigo Magazine}{Dec 2023 -- Present}
      {Web Development Officer \& Creative Director}{}
      \resumeItemListStart
        \resumeItem{\textbf{Provided direct user training and guidance} by developing an end-to-end article submission system, empowering non-technical writers to independently troubleshoot and format content.}
        \resumeItem{Enhanced the customer experience by proposing and implementing \textbf{product workflow optimizations}, ultimately adding 400+ new active users within the first month.}
        \resumeItem{Updated and maintained asset repositories and \textbf{technical documentation}, migrating media to a Cloudflare CDN to ensure reliable system uptime.}
      \resumeItemListEnd
    \resumeSubheading
      {Society of Hispanic Professional Engineers}{Oct 2023 -- Apr 2024}
      {Corporate Liaison}{}
      \resumeItemListStart
        \resumeItem{Secured \textbf{\$300} in funding through corporate partnerships to support student initiatives.}
        \resumeItem{Coordinated and hosted professional engagement events, expanding member access to networking and career opportunities.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{YourOwn} $|$ \emph{Team Lead \& System Architect}}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Integrated \textbf{automated system testing} suites to proactively identify data logic errors, ensuring continuous reliability and preventing recurring bugs from reaching end-users.}
        \resumeItem{\textbf{Collaborated cross-functionally} to manage dynamic UI configurations, resolving complex rendering issues and ensuring a high-quality user experience across all supported platforms.}
        \resumeItem{Documented structural logic and system architecture to serve as \textbf{reference material for internal teams}, improving long-term maintainability and troubleshooting efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical:} React, JavaScript, TypeScript, Java, Express, Prisma, Mongodb, Python, Docker, AWS, Postman \\
     \textbf{Design \& PM Tools:} Figma, Notion, Jira, Agile Workflow, UX Wireframing \\
     \textbf{Languages:} English, Spanish
    }}
 \end{itemize}
\end{document}
