%-------------------------
% Resume in Latex - Luis Alarcon (PM-focused version with YourOwn)
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\begin{document}
\begin{center}
    \textbf{\Huge \scshape Luis Alarcon} \\ \vspace{1pt}
    \small 936-828-9969 $|$ \href{mailto:alarconMandujanoLuis@gmail.com}{\underline{alarconMandujanoLuis@gmail.com}} $|$
    \href{https://www.linkedin.com/in/luis-alberto-alarcon-mandujano-68316b359}{\underline{linkedin}} $|$
    \href{https://github.com/LuisAlar}{\underline{github}} 

\end{center}
{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Dallas}{Dallas, TX}
      {Bachelor of Science in Software Engineering}{Expected May 2027}

  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Orbital Mentorship}{Nov 2024 -- Present}
      {DevOps Lead}{}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{Docker-based} deployment and onboarding solution using automation scripts, standardizing environments and reducing configuration time by \textbf{50\%} while virtually eliminating dependency errors.}
        \resumeItem{Built an in-house API observability and monitoring tool to identify network bottlenecks, enabling continuous performance tracking and reducing per-page network requests from 20 to 1–2.}
        \resumeItem{Architected a scalable backend data management system, optimizing querying and enabling high-performance CRUD operations for massive datasets.}
      \resumeItemListEnd
    \resumeSubheading
      {Xtensible Solutions}{Apr 2024 -- Aug 2024}
      {Solutions Engineer Intern}{}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Python automation scripts} to manage cloud instance creation, snapshot retrieval, and automated GitHub integration, significantly \textbf{reducing} manual deployment overhead.}
        \resumeItem{Integrated automated API testing workflows for functional and regression testing, ensuring high reliability and stability of web services before deployment.}
        \resumeItem{Accelerated QA feedback loops and continuous integration processes by systematically identifying and reporting system defects to engineering leadership.}
      \resumeItemListEnd
    \resumeSubheading
      {Indigo Magazine}{Dec 2023 -- Present}
      {Web Development Officer \& Creative Director}{}
      \resumeItemListStart
        \resumeItem{Architected an automated asset pipeline, migrating media from a static codebase to a \textbf{Cloudflare CDN} by creating a workflow to fetch and deploy assets from Box.}
        \resumeItem{Developed internal tools including an end-to-end article submission system, empowering users to upload content independently and significantly \textbf{reducing developer overhead}.}
        \resumeItem{Collaborated cross-functionally to scale the web platform, successfully handling high traffic spikes and adding \textbf{400+} new active users to the platform within the first month.}
      \resumeItemListEnd
    \resumeSubheading
      {Society of Hispanic Professional Engineers}{Oct 2023 -- Apr 2024}
      {Corporate Liaison}{}
      \resumeItemListStart
        \resumeItem{Secured \textbf{\$300} in funding through corporate partnerships to support student initiatives.}
        \resumeItem{Coordinated and hosted professional engagement events, expanding member access to networking and career opportunities.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{YourOwn} $|$ \emph{Team Lead \& System Architect}}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Spearheaded the migration from a monolithic file structure to a scalable, enterprise feature-based architecture, improving system maintainability and deployment modularity.}
        \resumeItem{Managed the integration of advanced server-side caching and state synchronization pipelines to ensure maximum uptime and performance for heavy data loads.}
        \resumeItem{Served as System Architect for a full-stack platform, managing component integrations and guiding architectural decisions to ensure 100\% data consistency across dynamic UI portfolios.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Cloud/DevOps Technologies:} Docker, AWS, Linux, Cloudflare CDN, CI/CD Principles \\
     \textbf{Programming \& Scripting:} Python, Java, JavaScript, TypeScript, Bash (familiar) \\
     \textbf{Frameworks \& Databases:} React, Node.js, Express, Prisma, MongoDB \\
     \textbf{PM \& Testing Tools:} Postman, Jira, Agile Workflow \\
     \textbf{Languages:} English, Spanish
    }}
 \end{itemize}
\end{document}

